Brief Announcement: An Improved Lower Bound for Dynamic Graph Partitioning

### 2020-01-29 paper/paper.tex
Greedy it should be (1)
minor

Let \emph{Greedy} be the algorithm that on each inter-cluster request
 moves to a perfect partition closest to the current one.
 That is,
 a partition reachable with the least number of node swaps.

@@

\begin{lemma} \label{lemma:k=3}
  The re-balancing cost for  Greedy algorithm for $k=3$ is $O(1)$.
  %\maciek{Greedy = find the cheapest (closest to the current) feasible partition}
  \label{rebalancing-cost}
\end{lemma}

>>>>

Let \emph{Greedy} be the algorithm that on each inter-cluster request
 moves to a perfect partition closest to the current one.
 That is,
 a partition reachable with the least number of node swaps from the current partition.

@@

\begin{lemma} \label{lemma:k=3}
  The re-balancing cost of Greedy for $k=3$ is $O(1)$.
  %\maciek{Greedy = find the cheapest (closest to the current) feasible partition}
  \label{rebalancing-cost}
\end{lemma}
